\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-24 tex/overview.tex
refactor most hierarchical network architectures section

\subsection{Most hierarchical network architectures maximize dynamical robustness}
Following the examples of the previous section, here we show, in general, that dynamical robustness is maximized for a given collection of SCCs by maximizing the number of links between them. This is accomplished by demonstrating that any graph $G$ with $l < l_{\mathrm{max}}$, where $l_{\mathrm{max}}$ refers to the maximum possible number of links between the given collection of SCCs, must have a lower dynamical robustness than one of the graphs having $l=l_{\mathrm{max}}$, referred to as $G_{\mathrm{max}}$, and that these $G_{\mathrm{max}}$ have SCCs related by the graph $G_{\mathrm{tot}}$ which gives the total ordering on those SCCs.

Examining the expression in \ref{eq:robschematic} and noting that $R_{\alpha}$ are all strictly less than one proves that networks maximizing $l$, will also maximize $R$.  Given two connected components $C_{\alpha}$ and $C_{\beta}$ with $v_{\alpha}$ and $v_{\beta}$ nodes respectively, we have a maximum of $v_{\alpha} v_{\beta}$ links going from $C_{\alpha}$ to $C_{\beta}$.  Hence, $l \le \sum_{(\alpha,\beta) \in \hier(G)} v_{\alpha} v_{\beta}$.  Since every acyclic digraph can be embedded into a totally ordered
set, we may assume without loss of generality that our components have
been ordered in a way such that, if $(\alpha,\beta) \in \hier(G)$, then $\alpha <
\beta$.  Hence, $l \le l_{\mathrm{max}}$ where
$$l_{\mathrm{max}} = \sum_{\alpha=1}^{n-1}\sum_{\beta=\alpha+1}^{n}v_{\alpha}
v_{\beta}~=~\frac{1}{2} \left( \sum_{\alpha=1}^{n} v_{\alpha} \right)^2-\frac{1}{2} \sum_{\alpha=1}^{n}
v_{\alpha}^2.$$
Suppose we have a graph $G$ with SCCs $C_1,\ldots,C_n$ and that $G_{\mathrm{tot}}$
is the graph on $n$ nodes with a link from node $i$ to node $j$ whenever $i < j$.  Then we have a graph $G_{\mathrm{max}}$ such that $\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$, the components of $G_{\mathrm{max}}$ are also $C_1, \ldots, C_n$, but that includes all possible links between each pair of components. In this case $R(G)~\le~R(G_{\mathrm{max}})$ for all $G \ne G_{\mathrm{max}}$ where $R(G_{\mathrm{max}})$ is equivalent to \ref{eq:robschematic} with $l_{\mathrm{max}}$ substituted for $l$
\begin{widetext}
\begin{align} \label{eq:sccmaxrobustness}
R(G_{\mathrm{max}}) =
\frac{\frac{1}{2} ((\sum_{\alpha=1}^n v_{\alpha})^2 - \sum_{\alpha=1}^n v_{\alpha}^2) +
                    \sum_{\alpha=1}^n \connectivity_{\alpha}
                    % \langle R(\hbox{stab}(C_i),\mu') \rangle_1
                R(C_{\alpha},S,\mu_{\alpha},\tau_{\alpha})}
     {\frac{1}{2} ((\sum_{\alpha=1}^n v_{\alpha})^2 - \sum_{\alpha=1}^n v_{\alpha}^2) +
                    \sum_{\alpha=1}^n \connectivity_{\alpha}}.
\end{align}
\end{widetext}
% where $R(G_{\mathrm{max}},S,\mu,\tau) = R_{\mathrm{max}}(C_1, \ldots C_n)$.
%This bound is attained by $G_{\mathrm{max}}$.
% $\langle R(\hbox{stab} (G_{\mathrm{max}}), \mu') \rangle_1 = R_{\mathrm{max}}(C_1, \ldots C_n)$.
\subsection{Simultaneous perturbation of multiple interaction strengths}
The results of the previous sections also hold when relationships between multiple system variables are perturbed simultaneously,
although the notation becomes more complicated.  Suppose that we
resample $m$ interactions.  Then the analog of \ref{eq:singleresamplemutau} is
\begin{equation}\label{eq:multipleresamplemutau}
\begin{aligned}
\tau^{(m)}(A' \mid A) &= \frac{1}{\binom{d}{m}} \sum_{i_1, \ldots, i_m}
  \tau^{(m)}_{i_1, \ldots, i_m} (A' \mid A), \\
\tau^{(m)}_{i_1, \ldots, i_m} (A' \mid A) &=
 \prod_{k=1}^m \rho_{i_k} (a'_{i_k})
 \prod_{j \notin \{i_1, \ldots i_m\}} \delta(a'_j - a_j).
\end{aligned}
\end{equation}
Now define
\begin{widetext}
\begin{equation*}
M = \left\{(m_0, m_1, \ldots, m_n) \,\bigg|\,
m = \sum_{i=0}^n m_i \quad\&\quad
m_0 \le \sum_{i=1}^{n-1} \sum_{j=i+1}^n \ell_{ij} \quad\&\quad
(\forall i \in \{1, \ldots, n\}) \; m_i < \connectivity_i \right\}.
\end{equation*}
\end{widetext}
Then, given $(m_0, m_1, \ldots, m_n) \in M$, there are ${m \choose
m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$ links from $C_i$ and
$m_0$ links between SCCs.  Hence, our
weighted average becomes
\begin{widetext}
\begin{equation}\label{eq:robustnessmultiple}
R(G, S, \mu, \tau^{(m)}) =
\frac{\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n}
      \left(m_0 + \sum\limits_{\alpha=1}^n m_\alpha R(C_\alpha, S, \mu, \tau^{(m_\alpha)}) \right)}
     {\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n} m}
\end{equation}
\end{widetext}

>>>>

\subsection{Most hierarchical network architectures maximize dynamical robustness}
Following the examples of the previous section, we now show, in general, that dynamical robustness is maximized for a given collection of SCCs by maximizing the number of links between them.  The proof consists of two stages; deriving an upper bound on the robustness of a network in terms of its SCCs and then showing that this bound is attained by a graph if and only if it maximizes the number of links between its SCCs.

Suppose we have a directed graph $G$ with SCCs $C_1,\ldots,C_n$.  Since every acyclic digraph can be embedded into a totally ordered set, we may assume without loss of generality that our components have been ordered in a way such that, if $(\alpha,\beta) \in \hier(G)$, then $\alpha < \beta$.  Given two connected components $C_{\alpha}$ and $C_{\beta}$ with $v_{\alpha}$ and $v_{\beta}$ nodes respectively, we have a maximum of $v_{\alpha} v_{\beta}$ links going from $C_{\alpha}$ to $C_{\beta}$.  Hence, $l \le l_{\mathrm{max}}$ where
$$l_{\mathrm{max}} = \sum_{\alpha=1}^{n-1}\sum_{\beta=\alpha+1}^{n}v_{\alpha}
v_{\beta}~=~\frac{1}{2} \left( \sum_{\alpha=1}^{n} v_{\alpha} \right)^2-\frac{1}{2} \sum_{\alpha=1}^{n}
v_{\alpha}^2.$$
Examining the expression in \ref{eq:robschematic} and noting that $R_{\alpha}$ are all strictly less than one leads to the conclusion that networks maximizing $l$ for a given set of SCCs, will also maximize $R$.  Hence, we have $R(G,S,\mu,\tau) \le R_{\mathrm{max}}$ where $R_{\mathrm{max}}$ is equivalent to \ref{eq:robschematic} with $l_{\mathrm{max}}$ substituted for $l$:
\begin{widetext}
\begin{align} \label{eq:sccmaxrobustness}
R_{\mathrm{max}} =
\frac{\frac{1}{2} ((\sum_{\alpha=1}^n v_{\alpha})^2 - \sum_{\alpha=1}^n v_{\alpha}^2) +
                    \sum_{\alpha=1}^n \connectivity_{\alpha}
                    % \langle R(\hbox{stab}(C_i),\mu') \rangle_1
                R(C_{\alpha},S,\mu_{\alpha},\tau_{\alpha})}
     {\frac{1}{2} ((\sum_{\alpha=1}^n v_{\alpha})^2 - \sum_{\alpha=1}^n v_{\alpha}^2) +
                    \sum_{\alpha=1}^n \connectivity_{\alpha}}.
\end{align}
\end{widetext}

Let $G_{\mathrm{tot}}$ refer to the directed graph on $n$ nodes with a link from node $i$ to node $j$ whenever $i < j$ and let $G_{\mathrm{max}}$ refer to the directed graph whose SCCs are $C_1, \ldots, C_n$, but which includes all possible links between each pair of components $C_\alpha, C_\beta$ when $\alpha < \beta$.  Then $\hier (G_{\mathrm{max}}) = G_{\mathrm{tot}}$ and $R(G_{\mathrm{max}}) = R_{\mathrm{max}}$.  Thus, we see that our bound $R_{\mathrm{max}}$ is attained by $G_{\mathrm{max}}$ so conclude that $R_{\mathrm{max}}$ is indeed the maximum value of dynamical robustness for any G-class of fixed points.  Furthermore, we note that for any other graph $G$, which has the maximum number of links between its SCCs, we also have $R(G) = R_{\mathrm{max}}$. By contrast, for any graph $G$, which has less than the maximum number of links between its SCCs, we have $R(G) < R_{\mathrm{max}}$.

\subsection{Simultaneous perturbation of multiple interaction strengths}
The results of the previous sections also hold when relationships between multiple system variables are perturbed simultaneously,
although the notation becomes more complicated.  Suppose that we
resample $m$ interactions, as a model for cases in which multiple interaction strengths among system variables are modified in a single timestep of the evolutionary process.  Then the analog of \ref{eq:singleresamplemutau} is
\begin{equation}\label{eq:multipleresamplemutau}
\begin{aligned}
\tau^{(m)}(A' \mid A) &= \frac{1}{\binom{d}{m}} \sum_{i_1, \ldots, i_m}
  \tau^{(m)}_{i_1, \ldots, i_m} (A' \mid A), \\
\tau^{(m)}_{i_1, \ldots, i_m} (A' \mid A) &=
 \prod_{k=1}^m \rho_{i_k} (a'_{i_k})
 \prod_{j \notin \{i_1, \ldots i_m\}} \delta(a'_j - a_j).
\end{aligned}
\end{equation}
Now define
\begin{widetext}
\begin{equation*}
M = \left\{(m_0, m_1, \ldots, m_n) \,\bigg|\,
m = \sum_{i=0}^n m_i \quad\&\quad
m_0 \le \sum_{i=1}^{n-1} \sum_{j=i+1}^n \ell_{ij} \quad\&\quad
(\forall i \in \{1, \ldots, n\}) \; m_i < \connectivity_i \right\}.
\end{equation*}
\end{widetext}
Then, given $(m_0, m_1, \ldots, m_n) \in M$, there are ${m \choose
m_0, m_1, \ldots. m_n}$ ways of choosing $m_i$ links from within $C_i$ and
$m_0$ links between SCCs.  Hence, our
weighted average becomes
\begin{widetext}
\begin{equation}\label{eq:robustnessmultiple}
R(G, S, \mu, \tau^{(m)}) =
\frac{\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n}
      \left(m_0 + \sum\limits_{\alpha=1}^n m_\alpha R(C_\alpha, S, \mu, \tau^{(m_\alpha)}) \right)}
     {\sum\limits_{(m_0, m_1, \ldots m_n) \in M}
      {m \choose m_0, m_1, \ldots. m_n} m}
\end{equation}
\end{widetext}
